Sakura Blossom Prediction Model for Japan

### 2024-12-04 paper/paper.qmd
Done!! Congratulation

The structure of this paper is as follows: @sec-data details the data sources and the methodologies employed, including data scraping and manipulation techniques. @sec-model outlines the development of prediction models, specifically Linear Regression and Bayesian Spline Models, which are further analyzed in @sec-result. In @sec-dis, the impact of global warming on the sakura blossom period, along with real-life implementation and limitations of the study, will be discussed, including an exploration of sakura flowering conditions from history to the present, and providing suggestions for further improvement. Further dataset and model details will be presented in @sec-sam and @sec-model-details separately.

@@

# Appendix {#sec-app}

## Sampling, Data Observational and Potential Bias
The survey design of this study integrates historical and modern sakura blossom datasets, providing a powerful framework for analyzing long-term trends and regional differences. And analyzed a survey from Statista on the purpose of visiting Japan, with over 32,364 participants, of which 13% of tourists came specifically for sakura blossoms [@arba2024travel]. The historical data, spanning 812 CE to 2015, focuses on Kyoto, where flowering dates have been reconstructed using historical documents, such as diaries and records of hanami events. These reconstructions were validated against observed data starting in 1881, ensuring reliability.

## Additional data details {#sec-sam}

### History Data

@@

### Correlation between Each Variable

@@

## Model details {#sec-model-details}

### Posterior predictive check

@@

>>>>

The structure of this paper is as follows: @sec-data details the data sources and the methodologies employed, including data scraping and manipulation techniques. @sec-model outlines the development of prediction models, specifically Linear Regression and Bayesian Spline Models, which are further analyzed in @sec-result. In @sec-dis, the impact of global warming on the sakura blossom period, along with real-life implementation and limitations of the study, will be discussed, including an exploration of sakura flowering conditions from history to the present, and providing suggestions for further improvement. Further dataset, model details, and dataset defect will be presented in @sec-sam, @sec-model-details, and @sec-def separately. An idealized survey for researching Sakura flowering in the context of socio-ecological dynamics is detailed in @sec-survey.

@@

# Appendix {-}

# Additional data details {#sec-sam}

## History Data

@@

## Correlation between Each Variable

@@

# Model details {#sec-model-details}

## Posterior predictive check

@@

# Sampling, Data Observational and Potential Bias {#sec-def}
The survey design of this study integrates historical and modern sakura blossom datasets, providing a powerful framework for analyzing long-term trends and regional differences. And analyzed a survey from Statista on the purpose of visiting Japan, with over 32,364 participants, of which 13% of tourists came specifically for sakura blossoms [@arba2024travel]. The historical data, spanning 812 CE to 2015, focuses on Kyoto, where flowering dates have been reconstructed using historical documents, such as diaries and records of hanami events. These reconstructions were validated against observed data starting in 1881, ensuring reliability.

# Idealized Methodology for Socio-Ecological Survey on Sakura Flowering {#sec-survey}

## Introduction

This appendix outlines an idealized survey methodology focused on public observations and opinions regarding sakura flowering patterns. The design prioritizes capturing data from underrepresented geographic areas in Japan, with a budget of up to $100,000.

## Sampling Strategy

To ensure balanced geographic representation, the survey will adopt a stratified random sampling approach focused on regions with limited historical sakura data.

- **Sampling Frame**: Residents and tourists in regions across Japan, particularly areas with limited sakura flowering records.
- **Sampling Method**: Stratified random sampling based on geographic distribution to address data gaps in underrepresented regions.
- **Sample Size**: Target 5,000 responses, adjusted for a 10% nonresponse rate to achieve approximately 4,500 usable responses.
- **Geographic Distribution**: Prioritize underrepresented areas (e.g., rural Hokkaido, Shikoku, and Kyushu) while maintaining coverage in major sakura observation regions like Kyoto and Tokyo.

## Recruitment Plan

The survey will be conducted exclusively online to maximize reach and cost efficiency:

- **Online Recruitment**:
  - Social media platforms (e.g., Instagram, X, Facebook) with region-specific campaigns targeting underrepresented areas.
  - Advertisements on sakura and climate-related blogs and websites, as well as platforms popular among nature enthusiasts and researchers.
  - Links to the survey hosted on platforms like Google Forms or similar secure systems.

## Budget Allocation
Online Recruitment Campaigns: $40,000        
Participant Incentives: $20,000       
Data Analysis and Quality Control:$15,000  
Administrative Costs: $15,000

**Total Budget**: $100,000

## Survey Design

The survey will focus on collecting neutral, scientifically relevant, and culturally appropriate data regarding sakura flowering patterns.

- **Question Types**: Close-ended and Likert-scale questions.
- **Response Options**: Neutral options, including “prefer not to say,” for sensitive questions.
- **Key Topics**:
  - Observations of sakura flowering patterns.
  - Perceptions of changes in flowering timing.
  - Opinions on influencing factors such as climate and geography.
  - Awareness of the connection between sakura flowering and climate change.

## Data Processing

The collected data will be cleaned, weighted, and analyzed to ensure quality and reliability:

1. **Prevent Duplicate Submissions**: Use unique IP tracking for online surveys.
2. **Handle Missing Data**: Remove responses with significant missing values.
3. **Weighting and Adjustment**: Apply equal weights for all regions to ensure balanced representation across geographic areas.
4. **Data Validation**: Pilot the survey with 50 respondents from targeted regions to refine the questions and ensure clarity.

## Example Survey Questions

1. Have you observed sakura flowering in your area in the past five years?
   - Yes
   - No
   - Prefer not to say
2. What is your gender
   - Male
   - Femae
   - Prefer not to say
3. Have you noticed changes in sakura flowering dates in your region over the past decade?
   - Yes, significantly earlier
   - Yes, slightly earlier
   - No noticeable change
   - Yes, slightly later
   - Yes, significantly later
4. What factors do you believe most influence sakura flowering patterns?
   - Temperature
   - Geographic location
   - Urban heat islands
   - Climate change
   - Other
5. Do you think sakura flowering patterns are a reliable indicator of climate change?
   - Strongly agree
   - Agree
   - Neutral
   - Disagree
   - Strongly disagree

## Conclusion

This survey methodology is designed to efficiently gather data about sakura flowering, with a focus on underrepresented geographic areas and public perceptions of influencing factors. By ensuring balanced representation and a cost-effective approach, the survey supports informed discussions on sakura flowering patterns and their broader implications, and may serves as a valuable foundation dataset for further research on socio-economic topics related to Sakura.
